\documentclass[conference]{IEEEtran}

\usepackage{url}
\usepackage{amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{balance}
\usepackage{caption}
\usepackage{subcaption}

\newcommand{\comment}[1]{{\textcolor{blue}{#1}}}


\usepackage{color,soul}

\newcommand{\todo}[1]{\hl{TODO:~#1}}
\renewcommand*\ttdefault{txtt} % the more modern typewriter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}


\title{SLOC: Service Level Objectives for Next Generation Cloud Comping}
%SUBTITLE
%\Large{}

\author{
	\IEEEauthorblockN{Stefan Nastic, Andrea Morichetti, \\ Thomas Pusztai, Schahram Dustdar}
	\IEEEauthorblockA{Distributed Systems Group, \\TU Wien, Vienna, Austria} 
									
\and	
	\IEEEauthorblockN{Deepak Vij, Futurewei Team}
	\IEEEauthorblockA{Futurewei Technologies, Inc., \\ Santa Clara CA USA}
}

% \IEEEoverridecommandlockouts

\maketitle
\begin{abstract}
In this paper we outline the general research challenges, aproaches, vision and roadmap for the SLOC project ....
Some citation for BibTex~\cite{nastic2014provisioning}
\todo{NOTE: IC papers have a limit of 5000 words.}
\end{abstract}

\begin{IEEEkeywords}
Service Level Objectives, Cloud Computing, Elasticity, Data Analytics 
\end{IEEEkeywords}

% Include expernal sections
\input{sections/introduction}

\section{Conclusion}
\label{sec:Conclusion}

\todo{Add conclusion.}

\section*{Acknowledgments}
This work is supported by \todo{SLOC}, under project No. \todo{XXX}.
\todo{Check with Margret about the project ref.}



\section*{About the authors}

\textbf{Stefan Nastic} is a Postdoctoral Research Assistant at the Distributed Systems Group (DSG), 
TU Wien, Austria.  He received his Dr. Tech. degree (equivalent PhD)
%in Software Engineering \& 	Internet Technologies, 
from TU Wien in 2016.  
%with a thesis titled: ''Programming, Provisioning and Governing IoT Cloud Systems``.
His research interests include: IoT and Edge Computing; 
Cloud Computing; Big Data Analytics; and Smart Cities.
%Nastic has been involved in several 
%EU-funded research projects such as SMART-FI, U-Test and SM4ALL, as well as, large 
%industrial projects such as Pacific Controls Cloud Computing Lab (PC3L). 
Contact him at snastic@infosys.tuwien.ac.at. \\

\textbf{Schahram Dustdar} 
is a full professor of computer science heading the DSG at TU 
Wien, Austria. His work focuses on Internet technologies. He is an IEEE Fellow, a member 
of the Academy Europeana, and an ACM Distinguished Scientist. Contact him at 
dustdar@dsg.tuwien.ac.at.\\

\todo{All: please add a short bio...}


\balance

\bibliographystyle{abbrv}
\bibliography{references}

\end{document}


